Working Title: Predicting Customer Behavior Using a Portuguese Financial Institution Dataset 

### 2024-06-22 code/eda-code/eda_my version.qmd
minor edit

#Comparing how age daa compares from those who subscribed to a term deposit and those
#that did not
ggplot(data=mydata)+
  geom_bar(mapping =aes(x=age))+
  facet_wrap(~y_termSubscribed, nrow=2)

@@

p12
```

@@

ggplot(pctjob, aes(x=reorder(job, numofYES), y=numofYES, fill=numofYES))+
  geom_bar(stat="identity")+
  coord_flip()

ggplot(pctjob, aes(x=reorder(job, (numofYES/numofBOTH)), y=(numofYES/numofBOTH)))+
  geom_bar(stat="identity")+
  coord_flip()

```
On the first figure, we can see that jobs with the most positive outcomes are management, technician, and blue-collar, but on the second chart we can see that the job-types with the
highest percentages are 'student', 'retired', and 'unemployed.' There appears to be a noticable different between the total number of positive cases, and the job types which are most commonly recording positive cases.

>>>>

figure_file = here("results", "figures", "yes-age.png")
ggsave(filename = figure_file, plot=p9)

figure_file = here("results", "figures", "yes-no-age.png")
ggsave(filename = figure_file, plot=p10)

#Comparing how age data compares from those who subscribed to a term deposit and those
#that did not
ggplot(data=mydata)+
  geom_bar(mapping =aes(x=age))+
  facet_wrap(~y_termSubscribed, nrow=2)

@@

p12
figure_file = here("results", "figures", "days-yes.png")
ggsave(filename = figure_file, plot=p12) 
```

@@

p13 = ggplot(pctjob, aes(x=reorder(job, numofYES), y=numofYES, fill=numofYES))+
  geom_bar(stat="identity")+
  coord_flip()

p14 = ggplot(pctjob, aes(x=reorder(job, (numofYES/numofBOTH)), y=(numofYES/numofBOTH), fill=numofYES))+
  geom_bar(stat="identity")+
  coord_flip()

figure_file = here("results", "figures", "jobs-count-yes.png")
ggsave(filename = figure_file, plot=p13) 
figure_file = here("results", "figures", "jobs-percent-yes.png")
ggsave(filename = figure_file, plot=p14)

p13
p14
```
On the first figure, we can see that jobs with the most positive outcomes are management, technician, and blue-collar, but on the second chart we can see that the job-types with the
highest percentages are 'student', 'retired', and 'unemployed.' There appears to be a noticable different between the total number of positive cases, and the job types which are most commonly recording positive cases.

### 2024-06-22 products/manuscript/Manuscript.qmd
minor edit

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
#resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
#knitr::kable(resulttable2)
```

>>>>

Example @tbl-resulttable4 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable4
#| tbl-cap: "Logistic regression model fit table."
#| echo: FALSE
resulttable4 = readRDS(here("results","tables","resulttable4.rds"))
knitr::kable(resulttable4)
```
